Document embedding trial

### 2020-08-21 outputs/documents/paper.Rmd
externalu consistency ngram

Language models underpinned by n-grams are widely applied in text prediction, spelling-correction, and machine translation (@brown1992class). In our application, we use a tri-gram based model to detect both real-word and non-word errors and correct them with the candidate word that has the highest probability.

@@

There are a variety of ways to implement an n-gram model within R @citeR including using R packages such as `Quanteda` (@citequanteda), `tidyText` (@citetidytext) and `tm` (@citetm). We used the Text Analysis Utilities, `tau`, R package @citetau because of we can separate text-cleaning and n-gram making in two different steps. We want to have control to manually clean the text because we want to add an end-of-sentence token to each sentence int he corpus. To illustrate the use of `tau`, we will first install and load the library, and create a small corpus.

@@

We will use the `textcnt()` function to turn the training corpus into tri-grams. The most important argument of this function is _corpus_, as well as _n_ to set the number of words in a sequence, _method_ to determine which type of counts to compute, and _split_ to designate the regular expression pattern for splitting. The function outputs a `textcnt` object, which is essentially a table with each tri-gram and their counts (@citetau).

@@

Here, we follow @falbel2017word to implement a skip-gram model of word2vec through Keras. There are three steps in the Keras deep learning framework: 1) prepare the data; 2) define the model; and 3) train and evaluate the model. **(Ke-Li: Can we change this to be a different dataset please?)** Following these steps, we first downloaded the **(Ke-Li: Is there a reason this is in brackets?)** [Amazon Fine Foods Reviews dataset from Stanford] [@amzfinefooddata] and preprocess the text into tokens.

**(Ke-Li: Add code.)**

@@

**(Ke-Li: Add code.)**

@@

**(Ke-Li: Add code.)**

@@

There are a variety of ways to implement GloVe word embedding models in R. One is to load GloVe embeddings into a frozen Keras Embedding layer [@kerasglove] using the `Keras` R package [@kerasR2020]. This means **(Ke-Li: Add what it means please.)** Another way, is to use the `text2vec` package [@text2vec].

@@

BERT is pre-trained by using two unsupervised tasks. The first task is Masked Language Model and and second task is Next Sentence Prediction. The bidirectional approach of BERT is alleviated by the "Masked Language Model" [@devlin2018bert]. The Masked Language Model masks certain words in the input corpus which forces the model to predict the original words by "filling in the blank". This training process blends the representation from the left and right context and therefore increases the model's context sensitivity [@nozza2020mask]. In the Next Sentence Prediction process, the model receives two sentences in sequence as input. 50% of the sentences are paired in the right sequence and the ones from the other half have sentences that are paired randomly [@devlin2018bert]. The goal of this process is to have BERT evaluate if the second sentence is the next sentence of the first sentence in the original text and sharpen its capacity to predict the likelihood of the next sentence.

@@

>>>>

Language models underpinned by n-grams are widely applied in text prediction, spelling-correction, and machine translation [@brown1992class]. In our application, we use a tri-gram based model to detect both real-word and non-word errors and correct them with the candidate word that has the highest probability.

@@

There are a variety of ways to implement an n-gram model within R @citeR including using R packages such as `Quanteda` [@citequanteda], `tidyText` [@citetidytext] and `tm` [@citetm]. We used the Text Analysis Utilities, `tau`, R package @citetau because of we can separate text-cleaning and n-gram making in two different steps. We want to have control to manually clean the text because we want to add an end-of-sentence token to each sentence int he corpus. To illustrate the use of `tau`, we will first install and load the library, and create a small corpus.

@@

We will use the `textcnt()` function to turn the training corpus into tri-grams. The most important argument of this function is _corpus_, as well as _n_ to set the number of words in a sequence, _method_ to determine which type of counts to compute, and _split_ to designate the regular expression pattern for splitting. The function outputs a `textcnt` object, which is essentially a table with each tri-gram and their counts [@citetau].

@@

Here, we follow @falbel2017word to implement a skip-gram model of Word2Vec through Keras. There are three steps in the Keras deep learning framework: 1) prepare the data; 2) define the model; and 3) train and evaluate the model. **(Ke-Li: Can we change this to be a different dataset please?)** Following these steps, we first downloaded the Google News dataset [@citegooglenews] and preprocess the text into tokens.

```{r, eval=FALSE}
tokenizer %>% fit_text_tokenizer(training_corpus)
```

@@

```{r, eval=FALSE}
skipgrams_generator <- function(text, tokenizer, window_size, negative_samples) {
  gen <- texts_to_sequences_generator(tokenizer, sample(text))
  function() {
    skip <- generator_next(gen) %>%
      skipgrams(
        vocabulary_size = tokenizer$num_words, 
        window_size = window_size, 
        negative_samples = 1
      )
    x <- transpose(skip$couples) %>% map(. %>% unlist %>% as.matrix(ncol = 1))
    y <- skip$labels %>% as.matrix(ncol = 1)
    list(x, y)
  }
}
```

@@

```{r, eval=FALSE}
model %>%
  fit_generator(
    skipgrams_generator(training_corpus, tokenizer, skip_window, negative_samples), 
    steps_per_epoch = 10, epochs = 1
  )
```

@@

There are a variety of ways to implement GloVe word embedding models in R. One is to load GloVe embeddings into a frozen Keras Embedding layer [@kerasglove] using the `Keras` R package [@kerasR2020]. This means the embedding vectors will not be updated during the training process. Another way, is to use the `text2vec` package [@text2vec].

@@

BERT is pre-trained by using two unsupervised tasks. The first task is Masked Language Model and and second task is Next Sentence Prediction. The bidirectional approach of BERT is alleviated by the "Masked Language Model" [@devlin2018bert]. The Masked Language Model masks random words in the input corpus which forces the model to predict the original words by "filling in the blank". This training process blends the representation from the left and right context and therefore increases the model's context sensitivity [@nozza2020mask]. In the Next Sentence Prediction process, the model receives two sentences in sequence as input. 50% of the sentences are paired in the right sequence and the ones from the other half have sentences that are paired randomly [@devlin2018bert]. The goal of this process is to have BERT evaluate if the second sentence is the next sentence of the first sentence in the original text and sharpen its capacity to predict the likelihood of the next sentence.

@@

For the task of text cleaning, fine-tuning is not required. The process of text cleaning involves detecting and correcting mis-spelled words. Correcting the incorrect words can be seen as predicting the correct words. The Masked Language Model of BERT can be employed to do such prediction. In the pre-training process, the Masked Language Model would mask random words to do the prediction. However, we can tell the model what we want to "mask" by assigning the words to be encoded as `[MASK]`. Consider the erroneous sentence that has ten words:

> "There was no possibility of taking a wlak that day."

Using a spell-checker, "wlak" is identified as an error and is substituted by `[MASK]`:

> "There was no possibility of taking a [MASK] that day."

The implementation of text correction with BERT in R with the `keras-bert` Python module is not yet completed. For the purpose of demonstrating how BERT predicts the missing words, we will show the implementation process in Python using the `pytorch_pretrained_bert` library. The reason to use `pytorch_pretrained_bert`(**Keli add citation**) instead of `keras-bert`is that `pytorch_pretrained_bert` has relatively comprehensive functions that makes the prediction of missing words more straightforward.

After we retrieved the new text data with the error replaced by `[MASK]`, we use the `tokenizer()` function in `pytorch_pretrained_bert` to tokenize the text:

```{python, eval=FALSE}
tokenized_text = tokenizer.tokenize("There was no possibility of taking a [MASK] that day.")
tokenized_text
>>> ['there', 'was', 'no', 'possibility', 'of', 'taking', 'a', '[MASK]', 'that', 'day', '.']
```

We then get the index of `[MASK]` within the sentence and save it to a list. Since we only have one `[MASK]` token, the list has only one element:

```{python, eval=FALSE}
mask_index = 7
```

`pytorch_pretrained_bert` has a dictionary of tokens generated from the pre-training stage. The tokens include the vocabulary, puncuations and special symbols. Each token in the dictionary is given an index, represented as `{token: index}`. The function `convert_tokens_to_ids()` encodes the tokens we got previously to their positional indices in the tokens dictionary and collects them into a list:

```{python, eval=FALSE}
indexed_tokens = tokenizer.convert_tokens_to_ids(tokenized_text)
indexed_tokens
>>> [2045, 2001, 2053, 6061, 1997, 2635, 1037, 103, 2008, 2154, 1012]
```

The next step is to encode the text by its segments. The model encodes a sentence of representing each word in the sentence with the positional index of the sentence in the provided corpus. For example, the example text has only one sentence "There was no possibility of taking a [MASK] that day." Therefore, the position of the sentence is "0", and the encoding for each word in the sentence, including the period is a series of "0" to the length of the sentence:

```{python, eval=FALSE}
segments_tokens = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
```

The previous two steps give us two set of encoding — `indexed_tokens` that contains the encoding for each token, and `segments_tokens` that contains the encoding for each sentence. These two encoding layers that we feed to BERT Masked Language Model. The model takes tensor objects as inputs [@paszke2017automatic], therefore we transformed the two lists into tensor objects before hands. These two tensor objects has two dimensions. The first dimension is the container, and the second dimension is the length of the token lists.

```{python, eval=FALSE}
tokens_tensor = torch.tensor([indexed_tokens])
tokens_tensor

segments_tensor = torch.tensor([segments_encodes])
segments_tensor
>>> [[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]]
```

The encoding layers can be represented as the following:

```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|        |'there' |'was' |'no' |'possibility'|'of'|'taking'|'a' |'[MASK]'|'that'|'day'| '.'|
|--------|--------|------|-----|-------------|----|--------|----|--------|------|-----|----|
|token   |2045    |2001  |2053 |6061         |1997|2635    |1037|103     |2008  |2154 |1012|
|segment |0       |0     |0    |0            | 0  |0       |0   |0       |0     |0    |0   |

We then load the pre-trained BertForMaskedLM and feed the two tensor objects to it. The model then returns a tensor object that has three dimensions. The `predictions` tensor objects contains the prediction score of all the words in the vocabulary.

```{python, eval=FALSE}
model = BertForMaskedLM.from_pretrained('bert-base-uncased')
predictions = model(tokens_tensor, segments_tensor)
predictions
```

To get the prediction, we will get the element with the highest prediction score and retrieve its index. The retrieved index is then used to find the corresponding token in the tokens dictionary. The predicted word is "walk", which matches with the original sentence in **Jane Eyre**.

```{python, eval=FALSE}
predicted_word_index = torch.argmax(predictions[0, mask_index]).item()
predicted_word_index
>>> 3328
predicted_word_token = tokenizer.convert_ids_to_tokens([predicted_index])[0]
predicted_word_token
>>> walk
```

### 2020-08-21 scripts/00-try_document_embedding.Rmd
externalu consistency ngram

```{r,warning=FALSE}
# Tokenize the abstract
abstracts <- read_csv("abstracts_101.csv")
tidy_abstracts <- abstracts %>%
  select(id, abstract) %>%
  unnest_tokens(word, abstract) %>%
  add_count(word) %>%
  filter(n >= 50) %>%
  select(-n)
```

@@

## Make the document matrix that contains document vectors
doc_matrix <- word_matrix_cast %*% glove_matrix
doc_matrix <- as.matrix(doc_matrix)
doc_matrix <- as.data.frame(doc_matrix)
doc_matrix <- cbind(doc_ids,doc_matrix ) # Put the document IDs back
doc_matrix
```
Up to this step, a document matrix with the corresponding vectors that represents the documentation is obtained. We can then perform matrix algera, or use the vectors to feed in machine learning algorithms for similarity detection or classfication. Further investigation is needed to perform the tasks!

>>>>

```{r,warning=FALSE}
# Tokenize the abstract
abstracts <- read_csv("input-abstracts.csv")
tidy_abstracts <- abstracts %>%
  select(id, abstract) %>%
  unnest_tokens(word, abstract) %>%
  add_count(word) %>%
  filter(n >= 50) %>%
  select(-n)
```

@@

## Make the document matrix that contains document vectors
doc_matrix <- word_matrix_cast %*% glove_matrix
doc_matrix <- as.matrix(doc_matrix)
doc_matrix <- as.data.frame(doc_matrix)
doc_matrix <- cbind(doc_ids,doc_matrix ) # Put the document IDs back
doc_matrix
```

Up to this step, a document matrix with the corresponding vectors that represents the documentation is obtained. We can then perform matrix algera, or use the vectors to feed in machine learning algorithms for similarity detection or classfication. Further investigation is needed to perform the tasks!
